---
title: "Developing Data Products_project"
author: "weimf"
date: "1/13/2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My app

In this project, I will create a Shiny application that assists you to choose your perfect diamonds. I use the `diamonds' dataset in R as the primary sources for analysis. The dataset contains the prices and other attributes of almost 54,000 diamonds and thus, should be informative.

## Data Used for analysis
There are 53,940 samples and 10 characteristics of the diamonds.  
Let's preview the data as below. In addition to the weight (carat) and size(x, y, z) that might affect the price of the diamond, the quality of cut, color, clarity are also determinants of the price of the diamond.
```{r, warning=FALSE}
library(ggplot2)
summary(diamonds)
```

## A general picture of the price by carat 

```{r, warning=FALSE}
library(ggplot2)

plot1 <- qplot(carat, price, data = diamonds, col = "red",
               main="The relationship between price and carat",
                xlab="carat",
                ylab="price")
plot1

```

## If you are looking for a diamond with the carat less than 0.5
### The relationship between price and quality of the cut

```{r}
newdata_1 <- subset(diamonds, carat <0.5)


plot2 <- boxplot(price~cut, data = newdata_1, col = "orange",
                 main="The relationship between price and quality of the cut",
                xlab="cut",
                ylab="price")
plot2


```

## If you are looking for a diamond with the carat less than 0.5
### The relationship between price and clarity
```{r}
plot5 <- boxplot(price~clarity, data = newdata_1, col = "blue",
                 main="The relationship between price and clarity",
                xlab="clarity",
                ylab="price")
plot5
```

## If you are looking for a diamond with the carat between 0.5 and 1
### The relationship between price and quality of the cut
```{r}
newdata_2 <- subset(diamonds, carat >=0.5 & carat < 1)

plot3 <- boxplot(price~cut, data = newdata_2, col = "orange",
                 main="The relationship between price and quality of the cut",
                xlab="cut",
                ylab="price")
plot3

```

## If you are looking for a diamond with the carat between 0.5 and 1
### The relationship between price and clarity
```{r}
plot6 <- boxplot(price~clarity, data = newdata_2, col = "blue",
                 main="The relationship between price and clarity of the cut",
                xlab="clarity",
                ylab="price")
plot6
```

## If you are looking for a diamond with the carat between 1 and 1.5
### The relationship between price and quality of the cut
```{r}
newdata_3 <- subset(diamonds, carat >=1 & carat < 1.5)

plot4 <- boxplot(price~cut, data = newdata_3, col = "orange",
                 main="The relationship between price and quality of the cut",
                xlab="cut",
                ylab="price")
plot4

```

## If you are looking for a diamond with the carat between 1 and 1.5
### The relationship between price and clarity
```{r}
plot7 <- boxplot(price~clarity, data = newdata_3, col = "blue",
                 main="The relationship between price and clarity of the cut",
                xlab="clarity",
                ylab="price")
plot7
```

## Let's apply the app to look for your perfect diamond

- The app developed for the the assignment is avalilable at: 
(https://weimf.shinyapps.io/myapp/)

- Files for developing the app and the presentation are avalilable on the GitHub: 
(https://github.com/weimf1990/Developing-Data-Products_project)


